Fastest Paths Between Points in $\R^2$ for a Particle Moving with Constant Speed and Bounded Centripetal Acceleration

### 2013-10-10 path_theorems.tex
In process of adding second two point proof.

\begin{theorem}
  \label{thm:line-proof}
  Given a particle $p \in \mathrm{R}^2$ with initial position of $\bvec{X_1}$ and no initial speed moving with bounded tangential acceleration, $a_t \le \bar{a}_{t}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
\end{theorem}

@@

>>>>

Note: we provide two nearly identical theorems with different proofs, to provide the reader with different ways to think about the problem.

\begin{theorem}\label{thm:line-proof}
  (John Wang's version)

  Given a particle $p \in \mathrm{R}^2$ with initial position of $\bvec{X_1}$ and no initial speed moving with bounded tangential acceleration, $a_t \le \bar{a}_{t}$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ lies on the line segment from $\bvec{X_1}$ to $\bvec{X_2}$:
\end{theorem}

@@

\begin{theorem}\label{thm:theta-zero}
  Given a particle $p$, if $\abs{\theta(t_1)} = 0$ at some time $t_$, then an optimal path, $\hat{\gamma}(t)$ has $\abs{\theta(t)} \ge 0$ for all $t \ge t_1$. Furthermore, given two valid paths, $\gamma_1(t)$ and $\gamma_2(t)$, then $T_f(\gamma_1) \le T_f(\gamma_2)$ if $\abs{\theta_1(t_1)} = 0$.
\end{theorem}

\end{proof}

\begin{theorem}
  (Jonathan Allen's version)

  Given a particle $p$ with initial position $\bvec{X_1}$, initial velocity $\bvec{v}(t)$, bounded tangential acceleration $a_t \le \bar{a}_t$, and infinite centripetal acceleration, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $\bvec{X_1}$ to $\bvec{X_2}$ is the line segment from $\bvec{X_1}$ to $\bvec{X_2}$.
\end{theorem}

  Define two particles, $p_1$ and $p_2$, that have the same initial conditions as particle $p$ in the Theorem statement.

  For some arbitrary $\epsilon > 0$. Define the centripetal acceleration of $p_1$ to be $a_{c, 1}$, and let $\bar{a_{c,\epsilon}}$ be the maximum value of $a_{c, 1}$ for $t \in [T_0, \epsilon]$. Now define the centripetal acceleration of $p_2$ to be

  \[
    a_c(t) = \begin{cases}
      \theta(T_0) / \epsilon \quad &\text{for} \quad t \in [T_0, T_0 + \epsilon]\\
      0 \quad &\text{for} \quad otherwise
    \end{cases}
  \]

  If we take the limit as $\epsilon \to \infty$, we get

  \[

  \]

  \begin{align}
    \theta_1(T_0(\gamma_1))& = \int_{t=T_0(\gamma_1)}^{T_0(\gamma_1)^+} \frac{d\abs{\phi(t')}}{dt} - \frac{\theta(T_0)}{\epsilon \v(t)} dt'\\
    & = 0 \quad \text{for} \quad \epsilon \to T_0
  \end{align}

  Furthermore,

  \begin{align}
    \theta_2(T_0)& = \int_{t=T_0(\gamma_1)}^{T_0(\gamma_1)^+} \frac{d\abs{\phi(t')}}{dt} - \frac{\theta(T_0)}{\epsilon \v(t)} dt'\\
    & = \theta(T_0)
  \end{align}

  From Theorem \ref{thm:theta-zero} we know that $\theta(t)$ must now be $0$, for all $t \ge T_0$, thus the particle is traveling in the $-\bhat{r}$ direction for $t \in [T_0, T_f]$, which is the line segment from $X_1$ to $X_2$.

\end{proof}
